Download, Compile and Link OpenBLAS Library with R

### 2020-12-11 README.Rmd
Update README.md

---
title: "Download, Compile and Link OpenBLAS Library with R"
author: |
  | **Author**: Prof. Dr. Pedro Rafael Diniz Marinho
  | **Package website**: **<https://prdm0.github.io/ropenblas>**
  |
  |
  |
  | **Summary**
output: 
  bookdown::github_document2:
    toc: true
toccolor: 'blue'
---

@@

@@

## 'ropenblas' function:

@@

### Details

@@

## 'last_version_r' function:

@@

## 'last_version_openblas' function:

@@

## 'rcompiler' function:

@@

## 'link_again' function:

@@

## 'rnews' function:

@@

# Advantages of using ropenblas package:

>>>>

---
title: "Download, Compile and Link OpenBLAS Library with R"
author: |
  | **Package website**: **<https://prdm0.github.io/ropenblas>**
  |
  |
  |
  | **Summary**
output: 
  bookdown::github_document2:
    number_sections: true
    toc: true
    toc_depth: 2
toccolor: 'blue'
---

@@

# Advantages of using ropenblas package

@@

## 'ropenblas' function

@@

**Details**

@@

## 'last_version_r' function

@@

## 'last_version_openblas' function

@@

## 'rcompiler' function

@@

## 'link_again' function

@@

## 'rnews' function

@@
